The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-13 paper.tex
Change the anisotropic part

The dielectric constant $\varepsilon$, although not well-defined for
monolayer 2D material, becomes applicable when the 2D layers are
stacked. \todo[inline]{I would appreciate for polishing this sentence}
In a bulk layered materil stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material, can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (see Figure \ref{fig-4}a):
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
The approximations come from the fact that
$\alpha_{\mathrm{Bulk}} \approx \alpha_{\mathrm{2D}}$, which can be
seen from the results of Figure \ref{fig-3}b and \ref{fig-3}c.  Note
that the effect of stacking is not considered in Eqs. \ref{eq:3D-para}
and \ref{eq:3D-perp}. We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (y-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(x-axis), as show in Figure \ref{fig-4}b and \ref{fig-4}c,
respectively, with data calculated at both HSE06 and PBE levels give
almost identical trends. We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} align along the line $y=x$ , with a
linear regression slope of 1.01 and $R^2$ of 0.97. On the other hand,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The difference for the prediction of
$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}, as also observed
in Figure \ref{fig-3}b, \ref{fig-3}c . With a better model describing
$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha^{\perp}$ and
the degree of interlayer coupling, the dielectric transition from 2D
to 3D would be smoothly described.

Although we have extensively shown that the treatment for the
dielectric nature differs in 2D (polarizability) and 3D (dielectric
constant) scenarios, a general picture of the dielectric properties in
both dimensions can still be drawn by studying the dielectric
anisotropy. The dielectric anisotropy index $\eta$ is defined as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange
square). The boundary separating the 2D and layered bulk materials is
determined using an linear support vector machine (SVM) classification
algorithm to be $y=0.048x+0.087$. The much lower $\eta$ values of 2D
materials compared with their bulk counterparts indicates a high
dielectric anisotropy, which is responsible for the unique 2D
optoelectronic properties, such as electrostatic transparency
\cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. We
also observe that $\eta$ of 2D materials increase almost linearly with
$E_{\mathrm{g}}$, while such trend is absent for layered bulk
materials. The observations above can be explained by the principles
presented in thie work. As a result from the limited layer thickness
(mostly 3--10 \AA{}), $\alpha^{\perp}$ of a monolayer 2D material
varies much less than $\alpha^{\parallel}$ (Figure \ref{fig-3}b and
\ref{fig-3}c), which explains the domination of $E_{\mathrm{g}}$ in
$\eta$ of 2D materials. On the other hand, the fact that
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ is generally larger than the
values calculated from $\alpha^{\perp}$ of monolayer due to interlayer
coupling (Figure \ref{fig-4}c), gives rise to larger $\eta$ for
layered bulk materials compared with the corresponding monolayer, and
making it possible to separate the 2D and layered bulk materials from
the $\eta-E_{\mathrm{g}}$ phase diagram. For comparison, we also
superimpose the dielectric anisotropy $\eta$ of common semiconducting
materials in other dimensions (details see Supplementary Section S4.5)
on the phase diagram in Figure \ref{fig:aniso}. Bulk covalent
materials (3D, e.g. GaN) and fullerenes (0D, e.g. C$_{60}$) show
isotropic dielectric property, scattered on the line $\eta=1$. On the
other hand, reduced dimensionality increases the dielectric anisotropy
of materials such as planar organic semiconductor (OSc, 1D-2D,
e.g. CuPc), carbon nanotube (CNT, 1D) and linear OSc (0D-1D,
e.g. polyacene). Interestingly, these materials also scatter along the
boundary line $y=0.048x+0.087$, indicating the criteria distinguishing
2D (more anisotropic) and bulk layered materials (more isotropic) from
the $\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
dimensions. From the phase diagram, we can see that 2D and bulk
layered materials (also including 2D van der Waals heterostructure
(vdWH) \cite{Novoselov_2016}), provides more flexibility in
controlling the dielectric and electronic properties, compared with
semiconductors in other dimensions.

\subsection{Implications for Experiments}
Finally, we would like to comment on the implications of this work for
the experiments concerning the dielectric properties of 2D materials.
As schematically shown in Figure \ref{fig-2D-3D}, the physical
quantities related to the dielectric properties can be categorized
into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
(iii) valid both 2D and 3D.  $\alpha$ and $\varepsilon$ are the
starting point for the strictly 2D and 3D quantities, which require
distinct definitions when dimensionality changes. Such quantities
include (but not limited to):
\begin{enumerate}
\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
  charge, polarization, electronic states, etc.

@@

\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
\end{enumerate}
These quantities have distinct units in both dimensions, and related
by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
plasma frequency), which requires prudent interpretation of
theoretical and experimental results. For instance, the experimentally
observed ``dielectric constant'' of monolayer 2D materials
\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
without considering the effect of mix ted medium. Instead, the 2D slab
polarizability, either transformed from the vacuum-containing
macroscopic dielectric constant, or predicted from the bandgap and
geometry as proposed here, will be a better descriptor for the true 2D
dielectric nature. On the other hand, there are also
dimension-independent quantities that valid for both 2D and 3D
systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
as well as the Hamaker constant of van der Waals interaction
$A_{\mathrm{H}}$. All these quantities are well-defined and can be
measured in both dimensions, while their relation with the dielectric
property varies with dimensionality. The well-known examples are the
different Wannier-Mott laws for exciton binding energy
\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
proposed here, and the distinct power laws for van der Waals
interactions \cite{Gobre_2013}. To get a accuracy description of
dielectric-related properties of the 2D materials and their
heterostructures, one has to distinguish between the 2D and 3D
properties, and choose a suitable relation with the
dimension-dependent and dimension-independent quantities.
\todo[inline]{I plan to use the original section for the ``implication for experiments''. Please help to add more on this part.}

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1_v110418i.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha^{\parallel}$ and
  $\alpha^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{SL}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{SL}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.65\linewidth]{img/fig2_v110418.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D
    materials}. \textbf{a}. $\alpha^{\parallel}$, $\alpha^{\perp}$
  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
  materials studied.  $\alpha^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
  schematically shown in the inset), showing a perfect linear relation
  with slope very close to $1/4\pi$. The universal scaling relation is
  also revealed using the C2DB database (squares), as superimposed on \textbf{b}
  and \textbf{c}.}
\end{figure}

% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
% \caption{\label{fig-delta} Scheme for the determination of the
  % covalent thickness of one-atom-thick (left) and few-atom-thick
  % (right) 2D materials.}
  % \end{figure}
\begin{table}[htbp]
  \centering
  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
    selected 2D materials calculated from first principles
    simulations. $r_{0}^{\parallel}$ is in general much larger than
    $r_{0}^{\perp}$, which accounts for the highly anisotropic
    dielectric nature of 2D materials.}
  \label{tbl:radii}  
  \begin{tabular}[htbp]{lcc}
    \hline
    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
    \hline
    2H-MoS$_{2}$ & 40.0 & 2.50 \\
    2H-MoSe$_{2}$ & &  \\
    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
    2H-WS$_{2}$ & 35.7 & 2.46  \\
    2H-WSe$_{2}$ & 41.0 & 2.71 \\
    2H-WTe$_{2}$ & 53.5 &  3.17\\
    \hline
  \end{tabular}
\end{table}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
      function of bandgap $E_{\mathrm{g}}$}. The
    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
    their bulk counterparts (orange square) can be distinguished by
    the line $y=0.048x+0.087$. $\eta-E_{\mathrm{g}}$ values of
    semiconducting materials in other dimensions are also superimposed
    for comparison. Isotropic dielectric property is observed for bulk
    covalent materials (3D, red triangle) and fullerenes (0D, green
    star), while reduced dimensional materials, including planar
    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
    scattered along the boundary line. The dimensionality and
    structure of typical materials are shown along the axis on the
    right. Compared with other materials, 2D materials and their bulk
    counterparts provide more flexibility of controlling the
    dielectric anisotropy.}
  \label{fig:aniso}
\end{figure}

>>>>

The dielectric constant $\varepsilon$, although not well-defined for
monolayer 2D material, becomes applicable when the 2D layers are
stacked. \todo[inline]{I would appreciate for polishing this sentence}
In a bulk layered materil stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material, can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (see Figure \ref{fig-4}a):
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
The approximations come from the fact that
$\alpha_{\mathrm{Bulk}} \approx \alpha_{\mathrm{2D}}$, which can be
seen from the results of Figure \ref{fig-3}b and \ref{fig-3}c.  Note
that the effect of stacking is not considered in Eqs. \ref{eq:3D-para}
and \ref{eq:3D-perp}. We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (y-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(x-axis), as show in Figure \ref{fig-4}b and \ref{fig-4}c,
respectively, with data calculated at both HSE06 and PBE levels give
almost identical trends. We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement, with a linear
regression slope of 1.01 and $R^2$ of 0.97. On the other hand,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}, as also observed
in Figure \ref{fig-3}b, \ref{fig-3}c . With a better model describing
$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
the degree of interlayer coupling, the dielectric transition from 2D
to 3D would be smoothly described.

Finally, we show that a general picture of the dielectric properties in
both dimensions can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha^{ii}}{\alpha^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangle) can be
clearly distinguished from the bulk layered materials (orange square)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as electrostatic
transparency \cite{Liluhua_2014,Tian_2016,Li_2018} and large exciton
binding energy
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy index
of corresponding 2D layer (details see Supplementary Section SXX
\todo{note}), which is the basis for the separation of bulk and 2D
regimes in the $\eta-E_{\mathrm{g}}$ phase diagram.  For comparison,
we also superimpose the dielectric anisotropy indices $\eta$ of common
semiconducting materials in other dimensions (details see
Supplementary Section S4.5) on the phase diagram in Figure
\ref{fig:aniso}. Bulk covalent (3D, e.g. Si, GaN) and 0D (fullerenes)
semiconductors show isotropic dielectric properties, scattered on the
line $\eta=1$. On the other hand, reduced dimensionality increases the
dielectric anisotropy of materials such as planar organic
semiconductor (OSc, 1D-2D, e.g. CuPc), carbon nanotube (CNT, 1D),
linear OSc (0D-1D, e.g. polyacene and polyacetylene). Interestingly,
most of these materials also scatter along the boundary line
separating the bulk and 2D regimes, indicating the criteria
distinguishing 2D (more anisotropic) and bulk layered materials (more
isotropic) from the $\eta-E_{\mathrm{g}}$ diagram, can also be applied
to other dimensions. From the phase diagram, we can see that 2D and
bulk layered materials (also including 2D van der Waals
heterostructure (vdWH) \cite{Novoselov_2016}), provides more
flexibility in controlling the dielectric and electronic properties,
compared with semiconductors in other dimensions.  \todo[inline]{I
  leave this section to be freely modified}

\subsection{Implications for Experiments}
\todo[inline]{Wait for comments from JC and MC.}
\iffalse
Finally, we would like to comment on the implications of this work for
the experiments concerning the dielectric properties of 2D materials.
As schematically shown in Figure \ref{fig-2D-3D}, the physical
quantities related to the dielectric properties can be categorized
into (i) strictly 2D (microscopic), (ii) strictly 3D (macroscopic) and
(iii) valid both 2D and 3D.  $\alpha$ and $\varepsilon$ are the
starting point for the strictly 2D and 3D quantities, which require
distinct definitions when dimensionality changes. Such quantities
include (but not limited to):
\begin{enumerate}
\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
  charge, polarization, electronic states, etc.

@@

\item The optical conductivity $\sigma_{\mathrm{2D}}$ and
  $\sigma_{\mathrm{3D}}$\cite{Bechstedt_2012,Matthes_2016}.
\end{enumerate}
These quantities have distinct units in both dimensions, and related
by $L$ (for density and optical conductivity) or $\sqrt{L}$ (for
plasma frequency), which requires prudent interpretation of
theoretical and experimental results. For instance, the experimentally
observed ``dielectric constant'' of monolayer 2D materials
\cite{Ning_2015,Li_2014,Yao_2014,Wu_2015} would be questionable
without considering the effect of mix ted medium. Instead, the 2D slab
polarizability, either transformed from the vacuum-containing
macroscopic dielectric constant, or predicted from the bandgap and
geometry as proposed here, will be a better descriptor for the true 2D
dielectric nature. On the other hand, there are also
dimension-independent quantities that valid for both 2D and 3D
systems, for instance the bandgap $E_{\mathrm{g}}$, exciton binding
energy $E_{\mathrm{b}}$, Bohr radius $r_{\mathrm{B}}$ of the exciton
as well as the Hamaker constant of van der Waals interaction
$A_{\mathrm{H}}$. All these quantities are well-defined and can be
measured in both dimensions, while their relation with the dielectric
property varies with dimensionality. The well-known examples are the
different Wannier-Mott laws for exciton binding energy
\cite{Olsen_2016_hydrogen}, the dielectric-bandgap relation
proposed here, and the distinct power laws for van der Waals
interactions \cite{Gobre_2013}. To get a accuracy description of
dielectric-related properties of the 2D materials and their
heterostructures, one has to distinguish between the 2D and 3D
properties, and choose a suitable relation with the
dimension-dependent and dimension-independent quantities.
\todo[inline]{I plan to use the original section for the ``implication for experiments''. Please help to add more on this part.}
\fi

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1_v110418i.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha^{\parallel}$ and
  $\alpha^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{SL}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{SL}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.65\linewidth]{img/fig2_v110418.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D
    materials}. \textbf{a}. $\alpha^{\parallel}$, $\alpha^{\perp}$
  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
  materials studied.  $\alpha^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
  schematically shown in the inset), showing a perfect linear relation
  with slope very close to $1/4\pi$. The universal scaling relation is
  also revealed using the C2DB database (squares), as superimposed on \textbf{b}
  and \textbf{c}.}
\end{figure}

% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
% \caption{\label{fig-delta} Scheme for the determination of the
  % covalent thickness of one-atom-thick (left) and few-atom-thick
  % (right) 2D materials.}
  % \end{figure}
\begin{table}[H]
  \centering
  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
    selected 2D materials calculated from first principles
    simulations. $r_{0}^{\parallel}$ is in general much larger than
    $r_{0}^{\perp}$, which accounts for the highly anisotropic
    dielectric nature of 2D materials.}
  \label{tbl:radii}  
  \begin{tabular}{lcc}
    \hline
    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
    \hline
    2H-MoS$_{2}$ & 40.0 & 2.50 \\
    2H-MoSe$_{2}$ & &  \\
    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
    2H-WS$_{2}$ & 35.7 & 2.46  \\
    2H-WSe$_{2}$ & 41.0 & 2.71 \\
    2H-WTe$_{2}$ & 53.5 &  3.17\\
    \hline
  \end{tabular}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.95\linewidth]{img/fig5.pdf}
  \caption{\textbf{Phase diagram of dielectric anisotropy $\eta$ as
      function of bandgap $E_{\mathrm{g}}$}. The
    $\eta$-$E_{\mathrm{g}}$ values of 2D materials (blue triangle) and
    their bulk counterparts (orange square) can be distinguished by
    the line $y=0.048x+0.087$. $\eta-E_{\mathrm{g}}$ values of
    semiconducting materials in other dimensions are also superimposed
    for comparison. Isotropic dielectric property is observed for bulk
    covalent materials (3D, red triangle) and fullerenes (0D, green
    star), while reduced dimensional materials, including planar
    organic semiconductor(OSc, 1D-2D, brown triangle), carbon nanotube
    (CNT, magenta circle) and linear OSc (0D-1D, violet pentagon) are
    scattered along the boundary line. The dimensionality and
    structure of typical materials are shown along the axis on the
    right. Compared with other materials, 2D materials and their bulk
    counterparts provide more flexibility of controlling the
    dielectric anisotropy.}
  \label{fig:aniso}
\end{figure}
